---
title: "Individual Trees Detecting using different methods"
format: html
editor: visual
---

::: panel-tabset
## Background

The Malcolm Knapp Research Forest (MKRF) is a 5,157-hectare forest located in Maple Ridge, British Columbia, approximately 60 km from Vancouver (The University of British Columbia, n.d.). Established in 1949, it serves as a world-class environment for research and education in forestry and sciences (The University of British Columbia, n.d.).

Individual tree detection (ITD) is a crucial technique in forest inventory and management for subsequent estimation of tree species, height, diameter, crown size and location (Luo et al., n.d). In this task, I am doing ITD using point cloud method and canopy height model derived method. The methods used in this tasks are based on Li et al., 2012 and Dalponte & Coomes, 2016.

## Objectives

The aim of this work is to apply 2 methods from Li et al. 2012 and Dalponte and Coomes 2016, which are point cloud method and CHM derived method.

## Data descriptions

-   LiDAR point cloud data

## References

Dalponte, M., & Coomes, D. A. (2016). Tree-centric mapping of forest carbon density from airborne laser scanning and hyperspectral data. Methods in Ecology and Evolution, 7(10), 1236-1245.

Li, W., Guo, Q., Jakubowski, M. K., & Kelly, M. (2012). A new method for segmenting individual trees from the lidar point cloud. Photogrammetric Engineering & Remote Sensing, 78(1), 75-84.

Luo, Z., Zhang, Z., Li, W., Chen, Y., Wang, C., Nurunnabi, A., & Li, J. (n.d). Detection of individual trees in UAV LiDAR point clouds using a deep learning framework based on multi-channel representation. IEEE Transactions on Geoscience and Remote Sensing, 59(7), 5769-5785.
:::

## Code

Load the necessary library

```{r, echo = TRUE, warning = FALSE, message = FALSE}
library(lidR)
library(terra)
library(tidyverse)
library(rgl)

```


Preparation of data for analysis

For this study, the LiDAR point cloud data, stored in .las files, had already been normalized. This pre-processing step simplifies subsequent analysis by adjusting the elevation values relative to the ground surface rather than absolute elevation.

```{r, echo = TRUE, warning = FALSE, message = FALSE}
# Read normalized .las file into catalog for further processing
norm_cat_mkrf <- readLAScatalog("C:/Users/hphung.stu/Downloads/GEM521/Labs/Lab 2/L2_data/Data/Normalized")

# Filter the points with height below 0m and above 65m
opt_filter(norm_cat_mkrf) <- '-drop_z_below 0 -drop_z_above 65'

```


```{r}



```













